### 2023-08-30 appendixPN.tex
section

For the sake of clarity, the construction detailled here concerns itself with reset Petri nets rather than reset-VASS. We recall that Petri nets and VASS are equivalents models~%\cite{qui?}
[??].

>>>>

For the sake of clarity, the construction detailled here concerns itself with reset Petri nets rather than reset-VASS. It is well-known that Petri nets and VASS are equivalents models with regards of the decidability of reachability problems: an $d$-VASS can be encoded into a Petri net with $d+2$ places and conversely, a Petri net with $p$ places can be encoded into a $p$-VASS~\cite{DBLP:journals/siglog/Schmitz16}.
